TITLE by YOUR_NAME_HERE
========================================================

> **Tip**: You will see quoted sections like this throughout the template to
help you construct your report. Make sure that you remove these notes before
you finish and submit your project!

> **Tip**: One of the requirements of this project is that your code follows
good formatting techniques, including limiting your lines to 80 characters or
less. If you're using RStudio, go into Preferences \> Code \> Display to set up
a margin line to help you keep track of this guideline!

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(PerformanceAnalytics)
library(dplyr)
library(RColorBrewer)
```

This report explores a dataset that contains data on approximately 5,000 
different white wines. Although I don't drink alcohol, I sometimes use it in 
cooking. I chose this dataset because white wine is the type of alcohol that I
have the most familiarity with.

```{r echo=FALSE, Load_the_Data}
# Load the Data
whiteWine = read.csv('wineQualityWhites.csv')
```

# Univariate Plots Section

```{r echo=FALSE, Describe_the_Data0}
dim(whiteWine)
```

```{r echo=FALSE, Describe_the_Data1}
str(whiteWine)
```

```{r echo=FALSE, Describe_the_Data2}
summary(whiteWine)
```

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

This dataset contains 11 attributes that describe white wine and one attribute
that is a rating of the quality of the white wine by a wine expert.

```{r echo=FALSE, Univariate_Plots1}
ggplot(aes(x=fixed.acidity), data=whiteWine) +
  geom_histogram(binwidth=.25)
```

```{r echo=FALSE, Univariate_Plots1.1}
ggplot(aes(x=fixed.acidity), data=whiteWine) +
  geom_histogram(binwidth=.25) +
  coord_cartesian(xlim=c(3.5, 10.5))
```

These histograms shows the distribution of tartaric acid in grams acid per 
liter of wine. 

```{r echo=FALSE, Univariate_Plots2}
ggplot(aes(x=volatile.acidity), data=whiteWine) +
  geom_histogram(binwidth=.02)
```

```{r echo=FALSE, Univariate_Plots2.1}
ggplot(aes(x=volatile.acidity), data=whiteWine) +
  geom_histogram(binwidth=.02) +
  coord_cartesian(xlim=c(0, .7))
```

These histograms show the distribution of acetic acid in the wines. The data is 
slightly skewed-right, but not enough to warrant a log transformation. Wines 
with high levels of volatile acidity may be good for cooking, since they often 
have a vinegar-like taste.

```{r echo=FALSE, Univariate_Plots3}
ggplot(aes(x=citric.acid), data=whiteWine) +
  geom_histogram(binwidth=.02)
```

```{r echo=FALSE, Univariate_Plots3.1}
ggplot(aes(x=citric.acid), data=whiteWine) +
  geom_histogram(binwidth=.02) +
  coord_cartesian(xlim=c(0, .8))
```

These histograms show the distribution of citric acid in the wines. I wonder 
how this affects the quality rating of the wines, if mediocre levels have 
higher quality ratings or not.

```{r echo=FALSE, Univariate_Plots4.1}
ggplot(aes(x=residual.sugar), data=whiteWine) +
  geom_histogram(binwidth=1)
```

```{r echo=FALSE, Univariate_Plots4.2}
ggplot(aes(x=residual.sugar), data=whiteWine) +
  geom_histogram(binwidth=.05) +
  scale_x_log10()
```

These histograms show the distribution of residual sugars found in the wines. 
I felt like the data was sufficiently skewed-right to try a log transformation 
on the data. We can see interesting bimodal behavior here. I would think that 
higher residual sugars would lead to a better tasting and thus better quality 
wine.

```{r echo=FALSE, Univariate_Plots5}
ggplot(aes(x=chlorides), data=whiteWine) +
  geom_histogram(binwidth=.005)
```

```{r echo=FALSE, Univariate_Plots5.1}
ggplot(aes(x=chlorides), data=whiteWine) +
  geom_histogram(binwidth=.005) +
  coord_cartesian(xlim=c(0, .1))
```

These histograms show the distribution of the chlorides or salt in the wines.

```{r echo=FALSE, Univariate_Plots6}
ggplot(aes(x=free.sulfur.dioxide), data=whiteWine) +
  geom_histogram(binwidth=5)
```

```{r echo=FALSE, Univariate_Plots6.1}
ggplot(aes(x=free.sulfur.dioxide), data=whiteWine) +
  geom_histogram(binwidth=2) +
  coord_cartesian(xlim=c(0, 100))
```

These plots show the distribution of free sulfur dioxide (this prevents 
microbial growth and oxidation of wines). 

```{r echo=FALSE, Univariate_Plots7}
ggplot(aes(x=total.sulfur.dioxide), data=whiteWine) +
  geom_histogram(binwidth=5)
```

```{r echo=FALSE, Univariate_Plots7.1}
ggplot(aes(x=total.sulfur.dioxide), data=whiteWine) +
  geom_histogram(binwidth=5) +
  coord_cartesian(xlim=c(0, 275))
```

These histograms show us the distibution of total sulfur dioxide. High levels 
of sulfur dioxide can affect the taste of wines.

```{r echo=FALSE, Univariate_Plots8}
ggplot(aes(x=density), data=whiteWine) +
  geom_histogram(binwidth=.001)
```

```{r echo=FALSE, Univariate_Plots8.1}
ggplot(aes(x=density), data=whiteWine) +
  geom_histogram(binwidth=.001) +
  coord_cartesian(xlim=c(.985, 1.005))
```

These plots show us the distribution of the density of the wines. Nothing 
really seems amiss here, the density of alcohol is less than that of water 
(which has a density of 1).

```{r echo=FALSE, Univariate_Plots9}
ggplot(aes(x=pH), data=whiteWine) +
  geom_histogram(binwidth=.02)
```

This distribution shows us the distribution of the pH levels of the wines. I 
would assume these correlate with the acidity values.

```{r echo=FALSE, Univariate_Plots10}
ggplot(aes(x=sulphates), data=whiteWine) +
  geom_histogram(binwidth=.01)
```

This histogram shows us the distribution of the sulphates in the wines. It is 
slightly skewed-right, but not very much.

```{r echo=FALSE, Univariate_Plots11}
ggplot(aes(x=alcohol), data=whiteWine) +
  geom_histogram(binwidth=.1)
```

```{r echo=FALSE, Univariate_Plots11.1}
ggplot(aes(x=alcohol), data=whiteWine) +
  geom_histogram(binwidth=.01) +
  scale_x_log10()
```

These plots show the distribution of the % alcohol of the wines. The data is 
slightly skewed-right, so I also plotted it with a log transformation. I don't 
know that the log transform really does anything to help us understand the 
data. It would be interesting to see how the % alcohol correlates with the 
quality score.

```{r echo=FALSE, Univariate_Plots12}
ggplot(aes(x=quality), data=whiteWine) +
  geom_histogram(binwidth=1)
```

This histogram shows the distribution of the quality scores of the wine. They 
were give on a scale from 0 to 10. The scores only fall between three and nine.

```{r echo=FALSE, Univariate_Plots13}
whiteWine = mutate(
  whiteWine, 
  dryness=factor(
    case_when(
      residual.sugar < 1 ~ 'bone_dry',
      residual.sugar < 17 ~ 'dry',
      residual.sugar < 35 ~ 'off_dry',
      residual.sugar < 120 ~ 'medium_sweet',
      residual.sugar >= 120 ~ 'sweet',
    )
  )
)
```

```{r echo=FALSE, Univariate_plots14}
whiteWine$dryness = factor(whiteWine$dryness,
                           levels=c('bone_dry',
                                    'dry',
                                    'off_dry',
                                    'medium_sweet',
                                    'sweet'))
```

I've heard people talk about a wine being dry. After doing some research, there 
are many levels of dryness, so I decided to create a factor to see how many 
types of wines were in the data set (the factors were based off of the 
infographic on this website 
https://winefolly.com/review/what-is-residual-sugar-in-wine/ ). Most of the 
wines that we have data for are dry. Since the distribution isn't even, I don't 
know how useful this factor will be.

```{r echo=FALSE, Univariate_Plots15}
whiteWine %>%
  group_by(dryness) %>%
  summarise(no_rows=length(dryness))
```

> **Tip**: Make sure that you leave a blank line between the start / end of
each code block and the end / start of your Markdown text so that it is
formatted nicely in the knitted text. Note as well that text on consecutive
lines is treated as a single space. Make sure you have a blank line between
your paragraphs so that they too are formatted for easy readability.

# Univariate Analysis

> **Tip**: Now that you've completed your univariate explorations, it's time to
reflect on and summarize what you've found. Use the questions below to help you
gather your observations and add your own if you have other thoughts!

### What is the structure of your dataset?

### What is/are the main feature(s) of interest in your dataset?

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

### Did you create any new variables from existing variables in the dataset?

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?


# Bivariate Plots Section

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

```{r echo=FALSE, Bivariate_Plots1}
round(cor(whiteWine), 2)
```

```{r echo=FALSE, Bivariate_Plots1}
chart.Correlation(whiteWine[c(2:13)], histogram=TRUE)
```

```{r echo=FALSE, Bivariate_Plots2}
ggplot(aes(x=fixed.acidity, y=volatile.acidity), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(4, 11), 
                  ylim=c(0, 0.8)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots3}
ggplot(aes(x=citric.acid, y=volatile.acidity), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0, .75), ylim=c(0.1, .6)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots4}
ggplot(aes(x=citric.acid, y=fixed.acidity), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0, .75), ylim=c(4, 11)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots5}
ggplot(aes(x=fixed.acidity, y=pH), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(4.5, 10.5), 
                  ylim=c(2.75, 3.75)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots6}
ggplot(aes(x=free.sulfur.dioxide, y=total.sulfur.dioxide), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0, 100), 
                  ylim=c(0, 300)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots7}
ggplot(aes(x=residual.sugar, y=density), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(1, 20), 
                  ylim=c(.985, 1.005)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots8}
ggplot(aes(x=alcohol, y=residual.sugar), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(8.5, 14), 
                  ylim=c(0.75, 20)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots9}
ggplot(aes(x=alcohol, y=density), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(8.5, 14), 
                  ylim=c(0.985, 1.005)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots10}
ggplot(aes(x=alcohol, y=quality), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(8.5, 14), 
                  ylim=c(3.5, 8.5)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots11}
ggplot(aes(x=volatile.acidity, y=quality), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0.1, 0.7), 
                  ylim=c(3.5, 8.5)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

```{r echo=FALSE, Bivariate_Plots12}
ggplot(aes(x=residual.sugar, y=quality), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0.5, 20), 
                  ylim=c(3.5, 8.5)) +
  geom_smooth(method='lm', color='red') +
  geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5))
```

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots0}
whiteWine$quality.factor = factor(whiteWine$quality)
```

```{r echo=FALSE, Multivariate_Plots1}
ggplot(aes(x=alcohol, y=residual.sugar), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, 25)) +
  scale_color_brewer()
```

```{r echo=FALSE, Multivariate_Plots2}
ggplot(aes(x=alcohol, y=quality.factor), data=whiteWine) +
  geom_point(aes(color=dryness)) +
  #coord_cartesian(ylim=c(0, 25)) +
  scale_color_brewer(palette='Dark2')
```

```{r echo=FALSE, Multivariate_Plots3}
ggplot(aes(x=quality.factor, y=alcohol), data=whiteWine) +
  geom_boxplot(aes(color=dryness)) +
  scale_color_brewer(palette='Dark2')
```

```{r echo=FALSE, Multivariate_Plots4}
ggplot(aes(x=alcohol/density, y=residual.sugar), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, 20)) +
  scale_color_brewer(palette='Greens')
```

```{r echo=FALSE, Multivariate_Plots5}
ggplot(aes(x=alcohol, y=volatile.acidity), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, .75)) +
  scale_color_brewer(palette='Purples')
```

```{r echo=FALSE, Multivariate_Plots6}
ggplot(aes(x=alcohol, y=volatile.acidity), 
       data=subset(whiteWine, dryness!='medium_sweet')) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, .75)) +
  scale_color_brewer(palette='Purples') +
  facet_wrap(~dryness) +
  aes(title='Facet Wrap by dryness')
```

```{r echo=FALSE, Multivariate_Plots7}
ggplot(aes(x=residual.sugar, y=total.sulfur.dioxide/alcohol), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(xlim=c(0, 20), ylim=c(0, 30)) +
  scale_color_brewer(palette='Reds')
```

```{r echo=FALSE, Multivariate_Plots8}
ggplot(aes(x=residual.sugar, y=total.sulfur.dioxide/alcohol), data=whiteWine) +
  geom_point(aes(color=dryness)) +
  coord_cartesian(xlim=c(0, 20), ylim=c(0, 30)) +
  scale_color_brewer(palette='Dark2') +
  facet_wrap(~quality.factor) +
  aes(title='Facet Wrap by quality')
```

```{r echo=FALSE, Multivariate_Plots9}
ggplot(aes(x=quality.factor, y=residual.sugar/alcohol), data=whiteWine) +
  geom_boxplot()
```

```{r echo=FALSE, Multivariate_Plots10}
ggplot(aes(x=quality.factor, y=volatile.acidity/alcohol), data=whiteWine) +
  geom_boxplot()
```

```{r echo=FALSE, Multivariate_Plots11}
ggplot(aes(x=quality.factor, y=citric.acid/residual.sugar), data=whiteWine) +
  geom_boxplot()
```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(aes(x=residual.sugar), data=whiteWine) +
  geom_histogram(binwidth=.05) +
  scale_x_log10() +
  aes(title='Log_10 of Residual Sugars')
```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(aes(x=alcohol, y=quality), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(8.5, 14), 
                  ylim=c(3.5, 8.5)) +
  geom_smooth(method='lm', color='red') +
  #geom_line(stat='summary', fun.y=quantile, fun.args=list(probs=.5)) +
  aes(title='% Alcohol vs. Quality Rating')
```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(x=residual.sugar, y=total.sulfur.dioxide/alcohol), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(xlim=c(0, 20), ylim=c(0, 30)) +
  scale_color_brewer(palette='Reds') +
  aes(title='Residual Sugars vs. Total Sulfur Dioxide/Alcohol and Quality')
```

### Description Three

------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!