Wine Exploration by Mack Damavandi
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(PerformanceAnalytics)
library(dplyr)
library(RColorBrewer)
```

This report explores a dataset that contains data on approximately 5,000 
different white wines. Although I don't drink alcohol, I sometimes use it in 
cooking. I chose this dataset because white wine is the type of alcohol that I
have the most familiarity with.

```{r echo=FALSE, Load_the_Data}
# Load the Data
whiteWine = read.csv('wineQualityWhites.csv')
```

# Univariate Plots Section

```{r echo=FALSE, Describe_the_Data0}
dim(whiteWine)
```

```{r echo=FALSE, Describe_the_Data1}
str(whiteWine)
```

```{r echo=FALSE, Describe_the_Data2}
summary(whiteWine[c(2:13)])
```

This dataset contains 11 attributes that describe white wine and one attribute
that is a rating of the quality of the white wine by a wine expert.

```{r echo=FALSE, Univariate_Plots1}
ggplot(aes(x=fixed.acidity), data=whiteWine) +
  geom_histogram(binwidth=.25)
```

```{r echo=FALSE, Univariate_Plots1.1}
ggplot(aes(x=fixed.acidity), data=whiteWine) +
  geom_histogram(binwidth=.25) +
  coord_cartesian(xlim=c(3.5, 10.5))
```

These histograms shows the distribution of tartaric acid in grams acid per 
liter of wine. 

```{r echo=FALSE, Univariate_Plots2}
ggplot(aes(x=volatile.acidity), data=whiteWine) +
  geom_histogram(binwidth=.02)
```

```{r echo=FALSE, Univariate_Plots2.1}
ggplot(aes(x=volatile.acidity), data=whiteWine) +
  geom_histogram(binwidth=.02) +
  coord_cartesian(xlim=c(0, .7))
```

These histograms show the distribution of acetic acid in the wines. The data is 
slightly skewed-right, but not enough to warrant a log transformation. Wines 
with high levels of volatile acidity may be good for cooking, since they often 
have a vinegar-like taste.

```{r echo=FALSE, Univariate_Plots3}
ggplot(aes(x=citric.acid), data=whiteWine) +
  geom_histogram(binwidth=.02)
```

```{r echo=FALSE, Univariate_Plots3.1}
ggplot(aes(x=citric.acid), data=whiteWine) +
  geom_histogram(binwidth=.02) +
  coord_cartesian(xlim=c(0, .8))
```

These histograms show the distribution of citric acid in the wines. I wonder 
how this affects the quality rating of the wines, if mediocre levels have 
higher quality ratings or not.

```{r echo=FALSE, Univariate_Plots4.1}
ggplot(aes(x=residual.sugar), data=whiteWine) +
  geom_histogram(binwidth=1)
```

```{r echo=FALSE, Univariate_Plots4.2}
ggplot(aes(x=residual.sugar), data=whiteWine) +
  geom_histogram(binwidth=.05) +
  scale_x_log10()
```

These histograms show the distribution of residual sugars found in the wines. 
I felt like the data was sufficiently skewed-right to try a log transformation 
on the data. We can see interesting bimodal behavior here. I would think that 
higher residual sugars would lead to a better tasting and thus better quality 
wine.

```{r echo=FALSE, Univariate_Plots5}
ggplot(aes(x=chlorides), data=whiteWine) +
  geom_histogram(binwidth=.005)
```

```{r echo=FALSE, Univariate_Plots5.1}
ggplot(aes(x=chlorides), data=whiteWine) +
  geom_histogram(binwidth=.005) +
  coord_cartesian(xlim=c(0, .1))
```

These histograms show the distribution of the chlorides or salt in the wines.

```{r echo=FALSE, Univariate_Plots6}
ggplot(aes(x=free.sulfur.dioxide), data=whiteWine) +
  geom_histogram(binwidth=5)
```

```{r echo=FALSE, Univariate_Plots6.1}
ggplot(aes(x=free.sulfur.dioxide), data=whiteWine) +
  geom_histogram(binwidth=2) +
  coord_cartesian(xlim=c(0, 100))
```

These plots show the distribution of free sulfur dioxide (this prevents 
microbial growth and oxidation of wines). 

```{r echo=FALSE, Univariate_Plots7}
ggplot(aes(x=total.sulfur.dioxide), data=whiteWine) +
  geom_histogram(binwidth=5)
```

```{r echo=FALSE, Univariate_Plots7.1}
ggplot(aes(x=total.sulfur.dioxide), data=whiteWine) +
  geom_histogram(binwidth=5) +
  coord_cartesian(xlim=c(0, 275))
```

These histograms show us the distibution of total sulfur dioxide. High levels 
of sulfur dioxide can affect the taste of wines.

```{r echo=FALSE, Univariate_Plots8}
ggplot(aes(x=density), data=whiteWine) +
  geom_histogram(binwidth=.001)
```

```{r echo=FALSE, Univariate_Plots8.1}
ggplot(aes(x=density), data=whiteWine) +
  geom_histogram(binwidth=.001) +
  coord_cartesian(xlim=c(.985, 1.005))
```

These plots show us the distribution of the density of the wines. Nothing 
really seems amiss here, the density of alcohol is less than that of water 
(which has a density of 1).

```{r echo=FALSE, Univariate_Plots9}
ggplot(aes(x=pH), data=whiteWine) +
  geom_histogram(binwidth=.02)
```

This distribution shows us the distribution of the pH levels of the wines. I 
would assume these correlate with the acidity values.

```{r echo=FALSE, Univariate_Plots10}
ggplot(aes(x=sulphates), data=whiteWine) +
  geom_histogram(binwidth=.01)
```

This histogram shows us the distribution of the sulphates in the wines. It is 
slightly skewed-right, but not very much.

```{r echo=FALSE, Univariate_Plots11}
ggplot(aes(x=alcohol), data=whiteWine) +
  geom_histogram(binwidth=.1)
```

```{r echo=FALSE, Univariate_Plots11.1}
ggplot(aes(x=alcohol), data=whiteWine) +
  geom_histogram(binwidth=.01) +
  scale_x_log10()
```

These plots show the distribution of the % alcohol of the wines. The data is 
slightly skewed-right, so I also plotted it with a log transformation. I don't 
know that the log transform really does anything to help us understand the 
data. It would be interesting to see how the % alcohol correlates with the 
quality score.

```{r echo=FALSE, Univariate_Plots12}
ggplot(aes(x=quality), data=whiteWine) +
  geom_histogram(binwidth=1)
```

This histogram shows the distribution of the quality scores of the wine. They 
were give on a scale from 0 to 10. The scores only fall between three and nine. Quality for wine is an interesting metric because it gives an objective value to something that is actually inherently subjective (see https://www.dummies.com/food-drink/drinks/wine/rating-wine-quality/ ).

```{r echo=FALSE, Univariate_Plots16}
whiteWine %>%
  group_by(quality) %>%
  summarise(no_rows=length(quality))
```

```{r echo=FALSE, Univariate_Plots13}
whiteWine = mutate(
  whiteWine, 
  dryness=factor(
    case_when(
      residual.sugar < 1 ~ 'bone_dry',
      residual.sugar < 17 ~ 'dry',
      residual.sugar < 35 ~ 'off_dry',
      residual.sugar < 120 ~ 'medium_sweet',
      residual.sugar >= 120 ~ 'sweet',
    )
  )
)
```

```{r echo=FALSE, Univariate_plots14}
whiteWine$dryness = factor(whiteWine$dryness,
                           levels=c('bone_dry',
                                    'dry',
                                    'off_dry',
                                    'medium_sweet',
                                    'sweet'))
```

I've heard people talk about a wine being dry. After doing some research, there 
are many levels of dryness, so I decided to create a factor to see how many 
types of wines were in the data set (the factors were based off of the 
infographic on this website 
https://winefolly.com/review/what-is-residual-sugar-in-wine/ ). Most of the 
wines that we have data for are dry. Since the distribution isn't even, I don't 
know how useful this factor will be.

```{r echo=FALSE, Univariate_Plots15}
whiteWine %>%
  group_by(dryness) %>%
  summarise(no_rows=length(dryness))
```

# Univariate Analysis

### What is the structure of your dataset?

There are 4,898 wines in the dataset with 12 attributes (fixed acidity, 
volatile acidity, citric acid, residual sugar, chlorides, free sulfur dioxide, 
total sulfur dioxide, density, pH, sulphates, alcohol, and quality).

I had a few other observations:

- 95.1% of the wines can be classified as dry.
- The median amount of residual sugar is 5.2 g/L and the max is 65.8 g/L.
- 92.6% of the wines have a quality rating of 5, 6, or 7 with the most of these
having a quality score of 6.

### What is/are the main feature(s) of interest in your dataset?

I would say that the man features of interest for me are citric acid, residual sugar, alcohol and quality. I don't think I'll be able to determine which wines are best for cooking from this dataset, but I think the right combination of these attributes would make for the highest quality wine.

### What other features in the dataset do you think will help support your \
###investigation into your feature(s) of interest?

I think that the volatile and fixed acidity may help support my investigation. The chlorides may also help.

### Did you create any new variables from existing variables in the dataset?

I have often heard people talk about a wine being 'dry.' The dryness of a wine can be determined by how much residual sugar there is in the wine. I created a factor based on some information I found. A wine with less than 1 g/L of residual sugar would be considered 'bone dry.' 'Dry' wines have between 1 g/L and 17 g/L residual sugar. 'Off dry' wines have up to 35 g/L residual sugar. 'Medium sweet' wines will have between 35 g/L residual sugar and 120 g/L residual sugar. Any wine with over 120 g/L residual sugar would be considered sweet. Most wines in this dataset would fall in the 'dry' category.

### Of the features you investigated, were there any unusual distributions? \
###Did you perform any operations on the data to tidy, adjust, or change the 
###form of the data? If so, why did you do this?

I was lucky and my dataset was already tidy and wasn't missing any data. I did perform a log transformation on the residual sugar and alcohol columns. The alcohol column wasn't very skewed-right and I didn't feel that the log transformation really helped me understand the data better. However, the transform of residual sugar was very interesting. The distribution appears to be bimodal with peaks at approximately 1.5 g/L and 10 g/L.


# Bivariate Plots Section

```{r echo=FALSE, Bivariate_Plots1}
round(cor(whiteWine[c(2:13)]), 2)
```

The residual sugar value has a strong correlation with density. The free sulfur dioxide and total sulfur dioxide also correlate, which makes sense since free sulfur dioxide is a subset of total sulfur dioxide. The strongest correlation with quality is the measure of alcohol in the wine which is also interesting.

```{r echo=FALSE, Bivariate_Plots1.1}
chart.Correlation(whiteWine[c(4:6,8:13)], histogram=TRUE)
```

I want to examine a little about the relationship between the acids listed in the dataset. It appears that volatile acidity and fixed acidity don't really correlate with each other.

```{r echo=FALSE, Bivariate_Plots2}
ggplot(aes(x=fixed.acidity, y=volatile.acidity), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(4, 11), 
                  ylim=c(0, 0.8)) +
  geom_smooth(method='lm', color='red')
```

Citric acid and volatile acidity have a slight negative correlation.

```{r echo=FALSE, Bivariate_Plots3}
ggplot(aes(x=citric.acid, y=volatile.acidity), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0, .75), ylim=c(0.1, .6)) +
  geom_smooth(method='lm', color='red')
```

Citric acid and fixed acidity have a slight positive correlation. I would guess that citric acid is probably a subset of fixed acidity.

```{r echo=FALSE, Bivariate_Plots4}
ggplot(aes(x=citric.acid, y=fixed.acidity), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0, .75), ylim=c(4, 11)) +
  geom_smooth(method='lm', color='red')
```

There is an interesting grouping of wines with a citric acid level of approximately 0.5 g/L. I wonder if all these wines are fermented in the same way or made by the same manufacturer. There could be some other scientific explanation as well.

We can also see the negative relationship between acidity and pH beow. As the fixed acidity increases pH decreases.

```{r echo=FALSE, Bivariate_Plots5}
ggplot(aes(x=fixed.acidity, y=pH), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(4.5, 10.5), 
                  ylim=c(2.75, 3.75)) +
  geom_smooth(method='lm', color='red')
```

We can also see the relationship between the free sulfur dioxide and the total sulfur dioxide. As stated above, this makes sense because free sulfur dioxide would be a subset of the total sulfur dioxide.

```{r echo=FALSE, Bivariate_Plots6}
ggplot(aes(x=free.sulfur.dioxide, y=total.sulfur.dioxide), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0, 100), 
                  ylim=c(0, 300)) +
  geom_smooth(method='lm', color='red')
```

The relationship between residual sugar and density was one that I didn't really think about beforehand, but it does make sense. The more sugar is left in the wine at the end of its fermentation process, the more weighty it will be and will thus have a greater density.

```{r echo=FALSE, Bivariate_Plots7}
ggplot(aes(x=residual.sugar, y=density), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(1, 20), 
                  ylim=c(.985, 1.005)) +
  geom_smooth(method='lm', color='red')
```

The correlation between residual sugar and alcohol is also interesting. I'm not sure why they would be negatively correlated.

```{r echo=FALSE, Bivariate_Plots8}
ggplot(aes(x=alcohol, y=residual.sugar), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(8.5, 14), 
                  ylim=c(0.75, 20)) +
  geom_smooth(method='lm', color='red')
```

After I did a little research, the correlation between density and alcohol also makes sense. Alcohol is less dense than water (which has a density of 1), so the more alcohol is in the wine, the less dense it will be.

```{r echo=FALSE, Bivariate_Plots9}
ggplot(aes(x=alcohol, y=density), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(8.5, 14), 
                  ylim=c(0.985, 1.005)) +
  geom_smooth(method='lm', color='red')
```

One of the most interesting relationships is that of alcohol to quality. In my mind, this could highlight the subjectivity of the quality scores that were given to the wine. 

```{r echo=FALSE, Bivariate_Plots10}
ggplot(aes(x=alcohol, y=quality), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(8.5, 14), 
                  ylim=c(3.5, 8.5)) +
  geom_smooth(method='lm', color='red')
```

There isn't any correlation between citric acid and the quality of the wine.

```{r echo=FALSE, Bivariate_Plots11}
ggplot(aes(x=citric.acid, y=quality), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0.1, 0.7), 
                  ylim=c(3.5, 8.5)) +
  geom_smooth(method='lm', color='red')
```

The correlation between the quality of the wine and the residual sugar is slightly negative. This is also counter-intuitive to me. As someone who doesn't drink wine, I would think that a little more sugar would make it more pleasant, but that seems not to be the case.

```{r echo=FALSE, Bivariate_Plots12}
ggplot(aes(x=residual.sugar, y=quality), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(0.5, 20), 
                  ylim=c(3.5, 8.5)) +
  geom_smooth(method='lm', color='red')
```

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
###investigation. How did the feature(s) of interest vary with other features \
###in the dataset?

For the most part, my features of interest really only had strong relationships with themselves. Citric acid was the only one that didn't really relate with anything besides the acidity values and pH. Both residual sugar and alcohol had a strong relationship with the density of the wine though, but I don't think density would really affect the quality of the wine, especially since it is still so close to the density of water. 

### Did you observe any interesting relationships between the other features \
###(not the main feature(s) of interest)?

I would have thought that the relationship between citric acid and volatile acidity would be positive, but it was negative. I would have to do some more research to understand why that is.

### What was the strongest relationship you found?

The strongest relationship that I found was between residual sugar and density, with a correlation coefficient of 0.84. The next strongest was between density and alcohol, with a correlation coefficient of -0.78.


# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots0}
whiteWine$quality.factor = factor(whiteWine$quality)
```

The new variable, quality.factor, factor in R based on the quality. Theredoesn't appear to be any significant grouping other than the higher quality wines typically having a higher alcohol content.

```{r echo=FALSE, Multivariate_Plots1}
ggplot(aes(x=alcohol, y=residual.sugar), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, 25)) +
  scale_color_brewer()
```

These plots use the other factor, dryness. It doesn't really appear to be the case that the dryness affects the quality of the rating at all.

```{r echo=FALSE, Multivariate_Plots2}
ggplot(aes(x=alcohol, y=quality.factor), data=whiteWine) +
  geom_point(aes(color=dryness)) +
  #coord_cartesian(ylim=c(0, 25)) +
  scale_color_brewer(palette='Dark2')
```

```{r echo=FALSE, Multivariate_Plots3}
ggplot(aes(x=quality.factor, y=alcohol), data=whiteWine) +
  geom_boxplot(aes(color=dryness)) +
  scale_color_brewer(palette='Dark2') +
  facet_wrap(~dryness) +
  aes(title='Facet wrap by dryness')
```

Plotting alcohol/density vs. residual sugar gives us a plot very similar to alcohol vs residual sugar. This makes sense since the density values are very close to 1.

```{r echo=FALSE, Multivariate_Plots4}
ggplot(aes(x=alcohol/density, y=residual.sugar), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, 20)) +
  scale_color_brewer(palette='Greens')
```

Since there isn't much of a relationship between citric acid and quality, it seems like the % alcohol is really pulling the darker points to the right on this plot.

```{r echo=FALSE, Multivariate_Plots5}
ggplot(aes(x=alcohol, y=citric.acid), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, .75)) +
  scale_color_brewer(palette='Purples')
```

I was also interested in how dryness might play a role. It is difficult to tell since so many of our observations are from dry wines.

```{r echo=FALSE, Multivariate_Plots6}
ggplot(aes(x=alcohol, y=citric.acid), 
       data=subset(whiteWine, dryness!='medium_sweet')) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, .75)) +
  scale_color_brewer(palette='Purples') +
  facet_wrap(~dryness) +
  aes(title='Facet Wrap by dryness')
```

The plot below is somewhat interesting. It seems like The higher quality wines (those rated 7 or above) are really pulled into the bottom right corner. Meaning that a low ratio of citric acid to sugar, and a high alcohol content would lead to a higher quality wine.

```{r echo=FALSE, Multivariate_Plots7}
ggplot(aes(x=alcohol, y=citric.acid/residual.sugar), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, .5)) +
  scale_color_brewer(palette='Reds')
```

I did a little more research on wine and found that the total sulfur dioxide can affect something called the 'nose' of the wine (basically the smell/taste relationship). It seems that the highest concentration of wines with quality scores 7 or above have total sulfur dioxide to alcohol rations between 5 and 20, with a lower residual sugar still giving a higher quality wine.

```{r echo=FALSE, Multivariate_Plots8}
ggplot(aes(x=residual.sugar, y=total.sulfur.dioxide/alcohol), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(xlim=c(0, 20), ylim=c(0, 30)) +
  scale_color_brewer(palette='Reds')
```

```{r echo=FALSE, Multivariate_Plots9}
ggplot(aes(x=residual.sugar, y=total.sulfur.dioxide/alcohol), data=whiteWine) +
  geom_point(aes(color=dryness)) +
  coord_cartesian(xlim=c(0, 20), ylim=c(0, 30)) +
  scale_color_brewer(palette='Dark2') +
  facet_wrap(~quality.factor) +
  aes(title='Facet Wrap by quality')
```

It appears the median residual sugar to alcohol ratio is lowest for quality 9 wines, but the median residual sugar to alcohol ratio for wines of quality 4 is also very low.

```{r echo=FALSE, Multivariate_Plots10}
ggplot(aes(x=quality.factor, y=residual.sugar/alcohol), data=whiteWine) +
  geom_boxplot()
```

The median citric acid to alcohol ratio is very similar for any quality of wine.

```{r echo=FALSE, Multivariate_Plots11}
ggplot(aes(x=quality.factor, y=citric.acid/alcohol), data=whiteWine) +
  geom_boxplot()
```

The median citric acid to residual sugar ratio is highest for wines of quality 9.

```{r echo=FALSE, Multivariate_Plots12}
ggplot(aes(x=quality.factor, y=citric.acid/residual.sugar), data=whiteWine) +
  geom_boxplot()
```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
###investigation. Were there features that strengthened each other in terms of \
##looking at your feature(s) of interest?

It was difficult to distinguish what attributes could accurately predict the quality of the wines. I would suggest that this probably has to do with the subjectivity of the quality score. The attribute that helped me see the best relationship was total sulfur dioxide to alcohol ratio. We could see a somewhat distinct grouping of higher quality wines.

### Were there any interesting or surprising interactions between features?

The most interesting interaction between features came when I plotted alcohol vs. citric acid to residual sugar ratio and colored the points by quality. The highest quality wines were pulled to the right and down, while the lowest quality wines were pulled to the left. This suggests that a higher quality wine wil have a low citric acid to residual sugar ratio along with a higher alcohol content.

------

# Final Plots and Summary

### Plot One

```{r echo=FALSE, Plot_One}
ggplot(aes(x=residual.sugar), data=whiteWine) +
  geom_histogram(binwidth=.05) +
  scale_x_log10() +
  aes(title='Log_10 of Residual Sugars') +
  labs(x='Residual Sugar in g/L',
       y='Number of Wines')
```

### Description One

The distribution of residual sugars appear to be bimodal on a log scale peaking at approximately 1.5 g/L and 10 g/L.

### Plot Two

```{r echo=FALSE, Plot_Two}
ggplot(aes(x=alcohol, y=quality), data=whiteWine) +
  geom_point(alpha=1/10, position='jitter') +
  coord_cartesian(xlim=c(8.5, 14), 
                  ylim=c(3.5, 8.5)) +
  geom_smooth(method='lm', color='red') +
  aes(title='% Alcohol vs. Quality Rating') +
  labs(x='% Alcohol',
       y='Quality Rating')
```

### Description Two

Wines with higher alcohol contents were typically scored higher than wines with lower alcohol contents.

### Plot Three

```{r echo=FALSE, Plot_Three}
ggplot(aes(x=alcohol, y=citric.acid/residual.sugar), data=whiteWine) +
  geom_point(aes(color=quality.factor)) +
  coord_cartesian(ylim=c(0, .5)) +
  scale_color_brewer(palette='Reds') +
  aes(title='% Alcohol vs. Citric Acid / Residual Sugar and Quality') +
  labs(x='% Alcohol',
       y='Citric Acid in g/L / Residual Sugar in g/L',
       color='Quality Rating')
```

### Description Three

Quality of wine could potentially be predicted by some kind of polynomic model, with alchol and the ratio of citric acid to residual sugar as the input variables.

------

# Reflection

I don't have much experience with wines, but it was very interesting to explore these 4,898 observations and the 12 variables that were gathered on them. I explored the quality of the wines across these variables.

This exploration was difficult. I struggled to find meaningful relationships that would appropriately predict the quality of wines. I believe that has to do with the subjectivity of the quality metric. If there was a more objective score, then it might be easier. But coming up with an objective score for something that is so personal would be hard to do.

For future iterations of this work, it would be interesting to build a model that could predict the quality based on some of the relationships that I found. I would also like to do some more research about which wines are best for cooking and see if that could be predicted from the 12 variables we have here.